\emeszida

### 2024-03-27 sigbovik/paper.tex
"Improved" acl abstract command to take an argument, allowing us to have a second cuneiform abstract.
A bit of introduction

@@

\section{Introduction}

\cite{robson2002}

>>>>

% % Needed for cuneiform abstract
% \newenvironment{cuneiformabstract}%
% 		 {\centerline{\large\bf Cuneiform Abstract}%
% 		  \begin{list}{}%
% 		     {\setlength{\rightmargin}{0.6cm}%
% 		      \setlength{\leftmargin}{0.6cm}}%
% 		   \item[]\ignorespaces%
% 		   \@setsize\normalsize{12pt}\xpt\@xpt
% 		   }%
% 		 {\unskip\end{list}}

@@

\begin{abstract}[\cuneiform{𒉆𒆸}]
test
\end{abstract}

\section{Introduction}
The history of math is long, but the history of programming is longer.
Cuneiform, arguably the first writing in the world, is known for its sheep receipts and beer ration lists as well as copper complaints \cite{oppenheim1954}.
This article adds neural network programming to that vaunted list of human achievements.
A newly discovered cuneiform tablet preserves the mechanism for performing simple neural network calculations.
These calculations, it seems, were used to calculate the lengths of triangles; a well known exercise preserved on the tablet known as Plimpton 322\footnote{And important and real introduction into this interesting object is found in \cite{robson2002}}.
It is remarkably that no historian of math or cuneiform scholar has ever consider this possibility.
This paper presents the story of discovery, a description of the cuneogramming language, and includes a facsimile copy of the important tablet as an appendix.
